AAAI Press Formatting Instructions \\for Authors Using \LaTeX{} --- A Guide

### 2021-09-14 publications/iaai21/dora_outlier_detection_iaai.tex
Update details describing planetary rover data set. (#42)

\subsubsection{Targets in Mars rover images.}
Mars exploration is fundamentally an exercise in discovery with the
goal of increasing our understanding of the history, evolution,
composition, and currently active processes on Mars.  Outliers
identified in Mars observations can inspire new discoveries and inform
the choice of which areas merit follow-up or deeper
investigation~\cite{kerner2020comparison,wagstaff:rover-novelty20}.
We collected \todo{XXX} images from the Navigation camera (Navcam) 
onboard the Mars Science Laboratory (MSL) rover
and employed the Rockster~\cite{burl:rockster16}
method currently used by onboard rover software to identify candidate rock
targets with an area of at least 100 pixels, yielding \num{6005}
targets.  We cropped out a \num{64}$\times$\num{64} pixel image
centered on each target.
%
We collaborated with an MSL science planning team member to
independently review the targets and identify those that were
considered novel by the mission ($n_{novel} = 108$).  Our goal for
this application is to assess how well the selections made by each
algorithm correlate with human novelty judgments to determine which
methods would be most suitable for informing onboard decisions about
follow-up observations.

@@

\subsubsection{Targets in Mars rover images.}
We simulated the operational setting in which the rover has observed
targets up through mission day (sol) $s$ and the goal is to rank all
subsequent targets (after sol $s$) to inform which recent targets
merit further study.  We organized the Mars target images
chronologically and partitioned them into the corresponding ``prior''
set $D_s$ and ``assessment'' set $D_{s+}$. We initialized each
algorithm with $D_s$ and requested a ranking of targets in $D_{s+}$.
\todo{Add table showing number (or percentage?) of novel targets in
the top $N$ selections, where $N$ = known number of novel targets in
$D_{s+}$.  And/or, report average rank of novel targets if alg ranks all
$|D_{s+}|$ targets. If time/room permits, do this for different values
of $s$.}

>>>>

\subsubsection{Targets in Mars rover images.}
Mars exploration is fundamentally an exercise in discovery with the
goal of increasing our understanding of the history, evolution,
composition, and currently active processes on Mars.  Outliers
identified in Mars observations can inspire new discoveries and inform
the choice of which areas merit follow-up or deeper
investigation~\cite{kerner2020comparison,wagstaff:rover-novelty20}.
We collected \num{72} images from the Navigation camera (Navcam) 
on the Mars Science Laboratory (MSL) rover
and employed the Rockster~\cite{burl:rockster16}
method currently used by onboard rover software to identify candidate rock
targets with an area of at least 100 pixels, yielding \num{1050}
targets.  We cropped out a \num{64}$\times$\num{64} pixel image
centered on each target.

We simulated the operational setting in which the rover has observed
targets up through mission day (sol) $s$ and the goal is to rank all
subsequent targets (after sol $s$) to inform which recent targets
merit further study.  We organized the Mars target images
chronologically and partitioned them into the corresponding ``prior''
set $D_s$ (sols \num{1343} to \num{1693}, $n=992$) and ``assessment''
set $D_{s+}$ (sols \num{1694} to \num{1703}, $n=58)$.

We collaborated with an MSL science planning team member to
independently review the targets in $D_{s+}$ and identify those that were
considered novel by the mission ($n_{outlier} = 9$).  Our goal for
this application is to assess how well the selections made by each
algorithm correlate with human novelty judgments to determine which
methods would be most suitable for informing onboard decisions about
follow-up observations.

@@

\subsubsection{Targets in Mars rover images.}
% We initialized each algorithm with $D_s$ and requested a ranking of
% targets in $D_{s+}$. 
\todo{Add table showing number (or percentage?) of novel targets in
the top $N$ selections, where $N$ = known number of novel targets in
$D_{s+}$.  And/or, report average rank of novel targets if alg ranks all
$|D_{s+}|$ targets. If time/room permits, do this for different values
of $s$.}
